Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support)\\ Technical Appendix Including Proofs and Details

### 2017-09-20 fully-abstract-comp/technical-report.tex
updated semantics of move (forgot the case where an int is moved to a register) + typos
typo
Removed subseg instruction. Not needed with the split instruction.
Removed the remainder of the old semantics (i.e. call and xjmp).

% Four arguments
\newcommand{\ssubseg}[4]{\fourinstr{\src{subseg}}{#1}{#2}{#3}{#4}}
\newcommand{\ssplit}[4]{\fourinstr{\src{split}}{#1}{#2}{#3}{#4}}

@@

% Four arguments
\newcommand{\tsubseg}[4]{\fourinstr{\trg{subseg}}{#1}{#2}{#3}{#4}}
\newcommand{\tsplit}[4]{\fourinstr{\trg{split}}{#1}{#2}{#3}{#4}}

@@

\dominique{7-9-2017: Should we keep local/global and linear/non-linear?  I was thinking just the latter would suffice...}
\lau{07-09-2017: The local/global mechanism still has some value as it now can be used for the purpose of arguments that cannot be stored by the receiver (if you are willing to ``pay'' the clearing cost). I do, however, not think that it is strictly necessary here to make things work.}
\lau{12-09-2017: I will remove the local capabilities today for the reasons we have discussed (they add to the complexity and they seem to be of little to no use without a clear memory instruction).}
Source language domains:
\[
  \begin{array}{rrcl}
   \addrbnf,\basebnf \in & \Addr & \defeq & \nats \\
    \sealbasebnf, \sigma \in & \Seal & \defeq & \nats \\
    &\Word & \defeq & \ints \uplus \SealableCaps\\
    \permbnf \in& \Perm & \defbnf & \dots \\
    &\linbnf & \defbnf & \linear \mid \normal \\
    &\aendbnf & \in & \Addr \uplus \{\infty \} \\
    &\sealendbnf & \in & \Seal \uplus \{\infty \} \\
    &\scbnf &\defbnf & ((\permbnf,\linbnf),\basebnf,\aendbnf,\addrbnf) \mid \seal{\linbnf,\sealbasebnf,\sealendbnf}\\
    & & & {\sourcecolor{} \mid \stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}}\\ 
    &\cbnf & \defbnf &  \scbnf \mid \sealed{\scbnf,\sigma}{\sourcecolor{} \; \mid \retptrd(\sigma) \mid \retptrc(\sigma)}\\ 
    &\RegName & \defbnf &\pcreg \mid \rret \mid \rstk \mid \rdata \mid \dots \\
    &\Reg & \defeq & \RegName \fun \Word\\
    &\Mem & \defeq & \Addr \fun \Word \\
    &\MemSeg & \defeq & \Addr \parfun \Word \\
    {\sourcecolor{} \sstkframe \in} & {\sourcecolor{} \StkFrame} & {\sourcecolor{} \defeq} & {\sourcecolor{} \Caps \times \MemSeg \times \Addr}\\
    \src{\sstk \in}& \src{ \Stack} & \src{ \defeq} & \src{ \StkFrame^*} \\
    \Phi \in & \ExecConf & \defeq & \Mem \times \Reg {\sourcecolor{} \; \times \; \Stack \times \MemSeg }\\
    &\Conf & \defeq & \ExecConf \uplus \{\failed\} \uplus (\{\halted\} \times \Mem)
  \end{array}
\]
\lau{06-09-2017: Should seals also have the option to be linear?}
\lau{13-09-2017: For now I have added linearity to the seals.}
The target language domains are all the non blue parts in the above. The source language domains are the black and blue parts in the above. Further
\begin{itemize}
\item $\linbnf$ defines domain $\Linear$
\item $\scbnf$ defines domain $\SealableCaps$
\item $\cbnf$ defines domain $\Caps$
\item $\Perm$ is defined as the set of permissions in Figure~\ref{fig:perm-hier}.
\end{itemize}

@@

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tsubseg{\trg{r}}{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{r}}{\trg{r}} \mid \\
  & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \mid \\ 
      & &   \tsplit{\trg{r}}{\trg{r}}{\trg{r}} \mid\tsplice{\trg{r}}{\trg{r}}{\trg{r}} 
\end{array}
\]

@@

\begin{align*}
  \sem{\tgetlin{r_1}{r_2}}(\Phi) = & 
                                   \begin{cases}
                                     \updPcAddr{\Phi\updReg{r_1}{\lin}} & 
                                     \arraycolsep=0pt
                                     \begin{array}[t]{l}
                                       \Phi(r_2) = ((\_,\lin),\_,\_,\_) \\
                                       \quad \src{\tor \Phi(r_2) = \stkptr{\_,\_,\_,\_} } \tand l = \linear\\
                                     \end{array} \\
                                     \updPcAddr{\Phi\updReg{r_1}{-1}} & \totherwise
                                   \end{cases}
\end{align*}
\lau{15-09-2017: Should getl do something for seals?}
\lau{15-09-2017: Do we want to allow getl and getp to work on sealed capabilities?}

\noindent\textbf{move}\\
\begin{align*}
  \sem{\tmove{r_1}{r_2}}(\Phi) = & 
                              \begin{cases}
                                \updPcAddr{\Phi\updReg{r_1}{\Phi(r_2)}} & \nonLinear{\Phi(r_2)}\\
                                \updPcAddr{\Phi\updReg{r_2}{0}\updReg{r_1}{\Phi(r_2)}} & \totherwise 
                              \end{cases}
\end{align*}
Notice that in the case where we are moving a linear capability and $r_1 = r_2$ the order of the updates matter.

@@

\noindent\textbf{subseg}\\
\lau{19-09-2017: TODO: I am not sure the way the end points are handled makes entirely sense. Have a look at it (maybe make a function that computes the end point?)}
  \sem{\tsubseg{r_1}{r_2}{r_3}{r_4}}(\Phi) = &
                                                 \Phi\updReg{r_2}{w_2}\updReg{r_1}{c} &
                                                   \text{for $i \in \{3, 4\}$ } \\
                                                   \quad \text{either $n_i = r_i$ or $n_i = \Phi.\reg(r_i)$}\\
                                                   \quad \text{and in either case $n_i \in \ints$ and} \\
                                                   \Phi(r_2) = ((\perm,\lin),\baddr,\eaddr,\aaddr) \tand \\
                                                   \baddr \leq n_3 \tand \\
                                                   (n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand \\
                                                   (n_2 = -42 \tand \eaddr = \infty) \Rightarrow \eaddr' = \infty \tand\\
                                                   \perm \neq \enter \tand\\
                                                   c = ((\perm,\lin),n_1,\eaddr',\aaddr)\\
                                                   w_2 = \linCons{\Phi(r_2)}
                                                 \end{array}
\\
                                                 \Phi\updReg{r_2}{w_2}\updReg{r_1}{c} &
                                                   \text{for $i \in \{3, 4\}$ } \\
                                                   \quad \text{either $n_i = r_i$ or $n_i = \Phi.\reg(r_i)$}\\
                                                   \quad \text{and in either case $n_i \in \ints$ and} \\
                                                   \Phi(r_2) = \seal{\lin,\sigma_\baddr,\sigma_\eaddr} \tand \\
                                                   \baddr \leq n_3 \tand \\
                                                   (n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand \\
                                                   (n_2 = -42 \tand \eaddr = \infty) \Rightarrow \eaddr' = \infty \tand\\
                                                   \perm \neq \enter \tand\\
                                                   c = \seal{\lin,n_1,\eaddr'}\\
                                                   w_2 = \linCons{\Phi(r_2)}
                                                 \end{array}
\\
                                                 \src{\Phi\updReg{r_2}{0}\updReg{r_1}{c}} &
                                                   \text{for $i \in \{3, 4\}$ } \\
                                                   \quad \text{either $n_i = r_i$ or $n_i = \Phi.\reg(r_i)$}\\
                                                   \quad \text{and in either case $n_i \in \ints$ and} \\
                                                   \Phi(r_2) = \stkptr{\perm,\baddr,\eaddr,\aaddr} \tand \\
                                                   \baddr \leq n_3 \tand \\
                                                   (n_2 \leq \eaddr \tand n_2 \in \nats) \Rightarrow \eaddr' = n_2 \tand\\
                                                   (n_2 = -42 \tand \eaddr = \infty) \Rightarrow \eaddr' = \infty \tand\\
                                                   \perm \neq \enter \tand\\
                                                   c = \stkptr{\perm,n_1,\eaddr',\aaddr}\\
                                                 \end{array}\right.\\

@@

                                  \eaddr_2 + 1 = \baddr_3 \tand \baddr_2 \leq \eaddr2 \tand \baddr_3 \leq \eaddr_3 \tand \\

@@

\subsubsection{Source Language}
\label{sec:source-language}
\lau{14-09-2017: This section will be obsolete when the unifyed definitions are done.}
\lau{23-03-2017: $\sjmp{}$ and $\scall{}{}$ needs an update. Update: they have been updated (It was $\sxjmp{}{}$ that needed an update.}

\textbf{Call}\\
Call has three cases, a successful call, undefined and failed. For a call to be successful, it needs two sealed capabilities - a data and a code capability. The code capability must be non-executable and the stack register must contain a stack pointer.
\lau{30-08-2017: Add more description here.}

For the call to be undefined, the conditions necessary for a legal call must be met and there must be an attempt at passing the stack pointer to the callee,
\dominique{7-9-2017: We declare the call to be undefined if the caller is doing something ``stupid'' that would break security but which we do not want to check for.  This includes: leaving a copy of the stack pointer or the old return pointer in a place accessible to the callee, invoking local callbacks (see discussion in POPL2018 submission of why this is bad).  The condition that $\cb_2 \neq \stkptr{\_,\_,\_,\_}$ is weird because this would not be the caller's fault, but the callee's.  Further thought needed regarding correct blame assignment for this case.}

If we are not in one of the two cases above, then the execution fails.
\begin{align*}
  \ssem{\scall{r_1}{r_2}} = & 
    \begin{cases}
      (\mem,\reg',\stk',\ms_\stk') & \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        % "red conditions" (in reference to blackboard picture)
                                        \Phi = (\mem,\reg,\stk,\ms_\stk) \text{ and } \\
                                        \Phi(r_1) = \sealed{\cb_1,\sigma} \text{ and } \\
                                        \Phi(r_2) = \sealed{\cb_2,\sigma} \text{ and } \\
                                        \nonExec{cb_2} \text{ and } \\
                                        \Phi(\rstk) = \stkptr{\perm, \stdrng, \aaddr} \text{ and } \\
                                        % "yellow conditions"
                                        \cb_2 \neq \stkptr{\_,\_,\_,\_} \text{ and } \\
                                        \noRetStkReg{\reg} \text{ and } \\
                                        \noRetStkMs{\ms_\stk'} \text{ and } \\
                                        \reg' = \reg
                                        \begin{array}[t]{l}
                                        \update{\pcreg}{\cb_1}\update{\rdata}{\cb_2}\\
                                        \update{\rretc}{\retptr}\\
                                        \update{\rstk}{\stkptr{\perm,[\aaddr,\eaddr],\aaddr}} \text{ and }
                                        \end{array}
\\                                        \text{ for $i \in \{1,2\}$ if $\isLinear{\Phi(r_i)}$, then $\reg''(r_i) = 0$ and} \\
                                        \opc = \Phi(\pcreg)\update{a}{\Phi(\pcreg).a+\calllen} \text{ and } \\
                                        \ms_\priv = \ms_\stk \setminus [\aaddr,\eaddr] \text{ and } \\
                                        \stk' = (\opc,\ms_\priv,\perm,\stdrng,\aaddr) :: \stk \text{ and } \\
                                        \ms_\stk' = \ms_\stk |_{[\baddr,\eaddr]}
                                      \end{array}\\
                                      & \\
      \tundefined & \arraycolsep=0pt
                                      \begin{array}[t]{l}
                                        % "red conditions" (reference to blackboard picture)
                                        \Phi = (\mem,\reg,\stk,\ms_\stk) \text{ and } \\
                                        \Phi(r_1) = \sealed{\cb_1,\sigma} \text{ and } \\
                                        \Phi(r_2) = \sealed{\cb_2,\sigma} \text{ and } \\
                                        \nonExec{cb_2} \text{ and } \\
                                        \Phi(\rstk) = \stkptr{\perm, \stdrng, \aaddr} \text{ and } \\
                                        % "yellow conditions"
                                        \text{not } \arraycolsep=0pt
                                        \left(\begin{array}{l}
                                          \cb_2 \neq \stkptr{\_,\_,\_,\_} \text{ and } \\
                                          \noRetStkReg{\reg} \text{ and } \\
                                          \noRetStkMs{\ms_\stk'}
                                        \end{array} \right)
                                      \end{array}\\
                                      & \\
      \failed & \text{otherwise}
    \end{cases}
\end{align*}

Unlike CHERI, we want sealed capabilies to be useable in a somewhat normal jump as well as the $\scall{}{}$. We cannot just use $\sjmp{}$ because it only takes one argument and we need to be able to jump to a code/data pair. To this end we introduce $\sxjmp{}{}$:
\begin{align*}
  \ssem{\sxjmp{r_1}{r_2}} = & 
                              \begin{cases}
                                \Phi'
                                \arraycolsep=0pt
                                \begin{array}[t]{l}
                                  [\reg.\pcreg \mapsto c_1] \\
                                  [\reg.\rdata \mapsto c_2]
                                \end{array} & 
                                \arraycolsep=0pt
                                \begin{array}[t]{l}
                                  \Phi(r_1) = \sealed{c_1,\sigma} \text{ and } \\
                                  \Phi(r_2) = \sealed{c_2,\sigma} \text{ and } \\
                                  \text{ for $i \in \{1,2\}$ if $\isLinear{c_i}$, then $\Phi'(r_i) = 0$} \\
                                  \text{ otherwise $\Phi'(r_i) = \Phi(r_i)$ and} \\
                                  \text{ $ \Phi(r) = \Phi'(r) \text{ for } r\in \tRegName \setminus \{r_1,r_2\}$ and} \\
                                  \nonExec{c_2}
                                \end{array}\\\\
%
                                (\mem,\reg',\stk',\ms_\stk') &
                                \arraycolsep=0pt
                                \begin{array}[t]{l}
                                  \Phi(r_1) = \retptrc \text{ and } \\
                                  \Phi(r_2) = \retptrd \text{ and } \\
                                  \Phi = (\mem, \reg, \stk, \ms_\stk) \text{ and } \\
                                  \stk = (\opc,\ms_\priv,\aaddr_\stk) :: \stk' \text{ and } \\
                                  \reg \arraycolsep=0pt
                                  \begin{array}[t]{l}
                                    \update{\pcreg}{\opc}\update{\rstk}{\stkptr{\dots,\aaddr_\stk}}\update{r_2}{0}\\
                                  \end{array}
                                \end{array}\\\\
%
                                \failed & \text{otherwise}
                              \end{cases}
\end{align*}
\lau{30-08-2017: questions: what do we allow to be left in the registers? Everything? Only global capabilities? Whatever we do should be matched in the compilation to the target.}

Notice, $\rdata$ serves the same function as the IDC register in CHERI, i.e.\ this is where the data capability is put. In the interpretation of $\sxjmp{}{}$, we require $c_2$ to be non-executable because CHERI does it. We are, however, not certain whether this requirement is strictly necessary (maybe it is dangerous to $\sxjmp{r}{r}$ where $r$ points to the same capability? Maybe it can be use to unseal a code capability by first sealing another code capability with the seal, $\sxjmp{}{}$ with the newly sealed and the old sealed capability. Now both capabilities are unsealed). CHERI also checks whether $c_1$ is executable and in range, but we do this on every step of the operational semantics, so we do not repeat that check.

>>>>

% Four arguments
%\newcommand{\ssubseg}[4]{\fourinstr{\src{subseg}}{#1}{#2}{#3}{#4}}
\newcommand{\ssplit}[4]{\fourinstr{\src{split}}{#1}{#2}{#3}{#4}}

@@

% Four arguments
%\newcommand{\tsubseg}[4]{\fourinstr{\trg{subseg}}{#1}{#2}{#3}{#4}}
\newcommand{\tsplit}[4]{\fourinstr{\trg{split}}{#1}{#2}{#3}{#4}}

@@

\dominique{7-9-2017: Should we keep local/global and linear/non-linear?  I was thinking just the latter would suffice...}
\lau{07-09-2017: The local/global mechanism still has some value as it now can be used for the purpose of arguments that cannot be stored by the receiver (if you are willing to ``pay'' the clearing cost). I do, however, not think that it is strictly necessary here to make things work.}
\lau{12-09-2017: I will remove the local capabilities today for the reasons we have discussed (they add to the complexity and they seem to be of little to no use without a clear memory instruction).}
Source language domains:
\[
  \begin{array}{rrcl}
   \addrbnf,\basebnf \in & \Addr & \defeq & \nats \\
    \sealbasebnf, \sigma \in & \Seal & \defeq & \nats \\
    &\Word & \defeq & \ints \uplus \SealableCaps\\
    \permbnf \in& \Perm & \defbnf & \dots \\
    &\linbnf & \defbnf & \linear \mid \normal \\
    &\aendbnf & \in & \Addr \uplus \{\infty \} \\
    &\sealendbnf & \in & \Seal \uplus \{\infty \} \\
    &\scbnf &\defbnf & ((\permbnf,\linbnf),\basebnf,\aendbnf,\addrbnf) \mid \seal{\linbnf,\sealbasebnf,\sealendbnf}\\
    & & & {\sourcecolor{} \mid \stkptr{\permbnf,\basebnf,\aendbnf,\addrbnf}}\\ 
    &\cbnf & \defbnf &  \scbnf \mid \sealed{\scbnf,\sigma}{\sourcecolor{} \; \mid \retptrd(\sigma) \mid \retptrc(\sigma)}\\ 
    &\RegName & \defbnf &\pcreg \mid \rret \mid \rstk \mid \rdata \mid \dots \\
    &\Reg & \defeq & \RegName \fun \Word\\
    &\Mem & \defeq & \Addr \fun \Word \\
    &\MemSeg & \defeq & \Addr \parfun \Word \\
    {\sourcecolor \sstkframe \in} & {\sourcecolor \StkFrame} & {\sourcecolor \defeq} & {\sourcecolor \Caps \times \MemSeg \times \Addr}\\
    \src{\sstk \in}& \src{ \Stack} & \src{ \defeq} & \src{ \StkFrame^*} \\
    \Phi \in & \ExecConf & \defeq & \Mem \times \Reg {\sourcecolor{} \; \times \; \Stack \times \MemSeg }\\
    &\Conf & \defeq & \ExecConf \uplus \{\failed\} \uplus (\{\halted\} \times \Mem)
  \end{array}
\]
\lau{06-09-2017: Should seals also have the option to be linear?}
\lau{13-09-2017: For now I have added linearity to the seals.}
The target language domains are all the non blue parts in the above. The source language domains are the black and blue parts in the above. Further
\begin{itemize}
\item $\linbnf$ defines domain $\Linear$
\item $\scbnf$ defines domain $\SealableCaps$
\item $\cbnf$ defines domain $\Caps$
\item $\Perm$ is defined as the set of permissions in Figure~\ref{fig:perm-hier}.
\end{itemize}

@@

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \nats \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{r}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{r}}{\trg{r}} \mid \\
  & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}}{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}}{\trg{r}} \mid \\ 
      & &   \tsplit{\trg{r}}{\trg{r}}{\trg{r}} \mid\tsplice{\trg{r}}{\trg{r}}{\trg{r}} 
\end{array}
\]

@@

\begin{align*}
  \sem{\tgetlin{r_1}{r_2}}(\Phi) = & 
                                   \begin{cases}
                                     \updPcAddr{\Phi\updReg{r_1}{\lin}} & 
                                     \arraycolsep=0pt
                                     \begin{array}[t]{l}
                                       \Phi(r_2) = ((\_,\lin),\_,\_,\_) \\
                                       \quad \src{\tor \Phi(r_2) = \stkptr{\_,\_,\_,\_} \tand l = \linear}\\
                                     \end{array} \\
                                     \updPcAddr{\Phi\updReg{r_1}{-1}} & \totherwise
                                   \end{cases}
\end{align*}
\lau{15-09-2017: Should getl do something for seals?}
\lau{15-09-2017: Do we want to allow getl and getp to work on sealed capabilities?}

\noindent\textbf{move}\\
\begin{align*}
  \sem{\tmove{r_1}{r_2}}(\Phi) = & 
                              \begin{cases}
                                \updPcAddr{\Phi\updReg{r_1}{r_2}} & r_2 \in \ints \\
                                \updPcAddr{\Phi\updReg{r_1}{\Phi(r_2)}} & \nonLinear{\Phi(r_2)}\\
                                \updPcAddr{\Phi\updReg{r_2}{0}\updReg{r_1}{\Phi(r_2)}} & \totherwise 
                              \end{cases}
\end{align*}
Notice that in the case where we are moving a linear capability and $r_1 = r_2$ the order of the updates matter.

@@

@@

@@
